# Introduction {#intro}

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
lapply(c("tidyverse", "googlesheets", "ggvis", "ggmap", "scales", "sp", "rgdal", "raster", "rnaturalearth", "rnaturalearthdata", "rnaturalearthhires", "jpeg", "png", "demogR", "popbio", "R2OpenBUGS", "ggthemes", "RColorBrewer", "dismo", "rgeos", "gridExtra", "rasterVis", "rasterImage", "blogdown", "bookdown"), require, character.only = TRUE)
```

## What is anthropology?

## Chapter/section labeling

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(arch).

## Figures and tables

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.


```{r echo=FALSE}
dnica <- read.csv("https://www.dropbox.com/s/lcn4p0j8anvlsiq/DominicaDemography%20-%20Sheet1.csv?dl=1")
dnica$sex <- ifelse(dnica$sex == 1, "Male", ifelse(dnica$sex == 2, "Female", "NA"))
```

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', warning=FALSE, message=FALSE}
p <- ggplot(dnica, aes(x = age, fill = sex)) + geom_histogram(position = "dodge", alpha = 0.6) + ggtitle("Historical Mortality Data", subtitle = "Recorded Age at Death")
p

# par(mar = c(4, 4, .1, .1))
# plot(pressure, type = 'b', pch = 3)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

## Citations with bookdown

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
